\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-23 paper/subdocuments/results.Rnw
legenden+design, robuster code

<<different_ginis>>=
df$G_reink[df$G_reink==1]<-NA
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("taxable income","income before deductions","taxable income after tax")
ggplot(dflong[dflong$kanton=="CH",], aes(x=steuerperiode,y=Gini,shape=Type))+
  scale_y_continuous(limits=c(0.18,0.4))+
  scale_x_continuous(limits=c(1982,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=Type),size=3)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Type))+
  theme_bw()+
  xlab("tax period")
#ggplot(dflong, aes(x=steuerperiode,y=Gini,colour=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")
@

@@

<<With and without equivalence scale>>=
library(ggplot2)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
ggplot(bdlong, aes(x=Jahr,y=Gini,shape=inc_def))+
  scale_y_continuous(limits=c(0.18,0.6))+
  scale_x_continuous(limits=c(1940,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=inc_def),size=3)+
  geom_line(data=bdlong,aes(linetype=inc_def))+
  theme_bw()+
  xlab("tax period")
@

@@

<<Comparing 2003 to 2010>>=
library(reldist)

@@

density1 <- density(bd.2003.ind$inc)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density",
     axes = FALSE,
     xlim = c(-50, 5000),
     ylim=c(0,0.0116031))
title(main="2003 vs 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(1200,1200),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("2003","2010"))
density2 <- density(bd.2010.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

The FTA stopped to publicly report data for special cases after tax period 1993/94. 
For more recent periods however we can compare already calculated percentiles provided by the FTA which are based on both special and normal cases to normal cases alone.
We will have a look at both, the 1993/94 period as the last period where both 
numbers were reported as well as 2010 where we compare data from the same source (FTA)
but based on different reporting (aggregated data vs. percentiles).

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- select(normal, -G_reink,-G_taxed,-ppop0,-G_steink0)
#normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 1993/94",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(100,100),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 1993/94"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<specialcases10, echo=FALSE,warning=FALSE>>=
library(foreign)
library(ggplot2)
#library(reldist)
normal <- filter(read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t"),kanton=="CH",steuerperiode==2010)
start <- which(names(normal)=="p1")
end <- which(names(normal)=="p99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,99)
normal <- data.frame(t(normal[1,start:end]),percentile)
names(normal)[1]=c("inc")

@@

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(120,120),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 2010"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<with_without_zeros,warning=FALSE>>=
dflong <- melt(df[,c("G_steink","G_steink0","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without zeros","including zeros")
ggplot(dflong[dflong$kanton=="CH" & dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,colour=Type))+geom_line(size=1)+theme_bw()+xlab("tax period")
ggplot(dflong[dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,colour=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")+theme(axis.text.x = element_text(angle = 60, hjust = 1))
@

@@

<<setup_data>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
library(reldist)
library(foreign)
# Get Brülhartdata for 2010
estv2010 <- read.csv("data/estv_normal_sonder_mitNuller_stE_2010.csv",sep=";")
###########################################
# Select percentiles for all cases (total)
estv2010.total<-estv2010[c(18:38),c(1,4)]
##
# Simulate individual data points
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), .01)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.total$Total,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.total$Total,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.total.ind<-data.frame(s)
names(estv2010.total.ind)[1]=c("inc")
estv2010.total.ind$inc<-estv2010.total.ind$inc/1000

@@

#####################################################
#         ACHTUNG: Bisher ohne Gewichte!            #
#####################################################

habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10<-data.frame(habe10$VerfuegbaresEinkommen08)
names(habe10)<-"inc_habe"
habe10$inc_habe[habe10$inc_habe<0]<-0 # One values is -20'000
habe10$inc_habe<-habe10$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-70, 4600),
     ylim=c(0,1.103e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(1.103e-02,1.103e-02))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.total.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

# Select married - HABE

habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.married<-habe0911 %.% 
  filter(Familientyp08>130,Jahr08==2010)
habe10.married<-data.frame(habe10.married$VerfuegbaresEinkommen08)
names(habe10.married)<-"inc_habe"
habe10.married$inc_habe[habe10.married$inc_habe<0]<-0 # One values is -20'000
habe10.married$inc_habe<-habe10.married$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10.married$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-257, 8000),
     ylim=c(0,0.0101390))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(0.0101390,0.0101390))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.married.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

# Select unmarried - HABE

habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.unmarried<-habe0911 %.% 
  filter(Familientyp08<140,Jahr08==2010)
habe10.unmarried<-data.frame(habe10.unmarried$VerfuegbaresEinkommen08)
names(habe10.unmarried)<-"inc_habe"
habe10.unmarried$inc_habe[habe10.unmarried$inc_habe<0]<-0 # One values is -20'000
habe10.unmarried$inc_habe<-habe10.unmarried$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-50, 2500),
     ylim=c(0,1.764e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(1200,1200),y=c(1.764e-02,1.764e-02))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.unmarried.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

>>>>

<<different_ginis>>=
df$G_reink[df$G_reink==1]<-NA
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("taxable income","income before deductions","taxable income after tax")
ggplot(dflong[dflong$kanton=="CH",], aes(x=steuerperiode,y=Gini,shape=Type))+
  scale_y_continuous(limits=c(0.18,0.4))+
  scale_x_continuous(limits=c(1982,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=Type),size=3)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Type))+
  theme_bw()+
  xlab("tax period")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))
#ggplot(dflong, aes(x=steuerperiode,y=Gini,colour=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")
@

@@

<<With and without equivalence scale>>=
library(ggplot2)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
ggplot(bdlong, aes(x=Jahr,y=Gini,shape=inc_def))+
  scale_y_continuous(limits=c(0.18,0.6))+
  scale_x_continuous(limits=c(1940,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=inc_def),size=3)+
  geom_line(data=bdlong,aes(linetype=inc_def))+
  theme_bw()+
  xlab("tax period")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))
@

@@

<<Comparing 2003 to 2010>>=
library(reldist, quietly=TRUE, warn.conflicts = FALSE)

@@

density1 <- density(bd.2003.ind$inc)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density",
     axes = FALSE,
     xlim = c(-50, 5000),
     ylim=c(0,0.0116031))
title(main="2003 vs 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(1200,1200),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("2003","2010"))
density2 <- density(bd.2010.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

The FTA stopped to publicly report data for special cases after tax period 1993/94. 
For more recent periods however we can compare already calculated percentiles provided by the FTA\footnote{These calculations were done on commission of the FTA within the SNF project Sinergia Nr. 130648 "The Swiss Confederation: A Natural Laboratory for Research on Fiscal and Political Decentralization" by Raphael Parchet and Stefanie Brilon in coordination with Prof. Dr. Marius Brülhart.} which are based on both special and normal cases to normal cases alone.
We will have a look at both, the 1993/94 period as the last period where both 
numbers were reported as well as 2010 where we compare data from the same source (FTA)
but based on different reporting (aggregated data vs. percentiles).

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE,hide=TRUE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- select(normal, -G_reink,-G_taxed,-ppop0,-G_steink0)
#normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 1993/94",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(60,60),y=c(0.019,0.019))
legend(fig1legend,lty=1:2, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
a<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 1993/94"))
abline(h=1,lty=2)
b<-reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
c<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<specialcases10, echo=FALSE,warning=FALSE,hide=TRUE>>=
library(foreign)
library(ggplot2)
#library(reldist)
normal <- filter(read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t"),kanton=="CH",steuerperiode==2010)
start <- which(names(normal)=="p1")
end <- which(names(normal)=="p99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,99)
normal <- data.frame(t(normal[1,start:end]),percentile)
names(normal)[1]=c("inc")

@@

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(65,65),y=c(0.016,0.016))
legend(fig1legend,lty=1:2, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
a<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 2010"))
abline(h=1,lty=2)
b<-reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
c<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<with_without_zeros,warning=FALSE>>=
dflong <- melt(df[,c("G_steink","G_steink0","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without zeros","including zeros")
ggplot(dflong[dflong$kanton=="CH" & dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+geom_line(size=1)+theme_bw()+xlab("tax period")+theme(legend.justification=c(0,1),legend.position=c(0, 1))
ggplot(dflong[dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")+theme(axis.text.x = element_text(angle = 60, hjust = 1))+theme(legend.justification=c(1,0),legend.position=c(1, 0))
@

@@

<<setup_data>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
library(reldist, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
# Get Brülhartdata for 2010
estv2010 <- read.csv("../../data/estv_normal_sonder_mitNuller_stE_2010.csv",sep=";")
###########################################
# Select percentiles for all cases (total)
estv2010.total<-estv2010[c(18:38),c(1,4)]
##
# Simulate individual data points
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), .01)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.total$Total,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.total$Total,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.total.ind<-data.frame(s)
names(estv2010.total.ind)[1]=c("inc")
estv2010.total.ind$inc<-estv2010.total.ind$inc/1000

@@

#####################################################
#         ACHTUNG: Bisher ohne Gewichte!            #
#####################################################
try(habe0911<-read.table("C:/Users/Hackstutz/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10<-data.frame(habe10$VerfuegbaresEinkommen08)
names(habe10)<-"inc_habe"
habe10$inc_habe[habe10$inc_habe<0]<-0 # One values is -20'000
habe10$inc_habe<-habe10$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-70, 4600),
     ylim=c(0,1.103e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(1.103e-02,1.103e-02))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.total.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

# Select married - HABE
try(habe0911<-read.table("C:/Users/Hackstutz/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.married<-habe0911 %.% 
  filter(Familientyp08>130,Jahr08==2010)
habe10.married<-data.frame(habe10.married$VerfuegbaresEinkommen08)
names(habe10.married)<-"inc_habe"
habe10.married$inc_habe[habe10.married$inc_habe<0]<-0 # One values is -20'000
habe10.married$inc_habe<-habe10.married$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10.married$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-257, 8000),
     ylim=c(0,0.0101390))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(0.0101390,0.0101390))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.married.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

# Select unmarried - HABE
try(habe0911<-read.table("C:/Users/Hackstutz/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.unmarried<-habe0911 %.% 
  filter(Familientyp08<140,Jahr08==2010)
habe10.unmarried<-data.frame(habe10.unmarried$VerfuegbaresEinkommen08)
names(habe10.unmarried)<-"inc_habe"
habe10.unmarried$inc_habe[habe10.unmarried$inc_habe<0]<-0 # One values is -20'000
habe10.unmarried$inc_habe<-habe10.unmarried$inc_habe*12/1000 # transform from monthly income to income per year

@@

density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-50, 2500),
     ylim=c(0,1.764e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(1200,1200),y=c(1.764e-02,1.764e-02))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.unmarried.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)
